Deep Variation Transformation for Foreground Detection

### 2019-03-11 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.
 On branch master
 Changes to be committed:
	modified:   draft.log
	modified:   draft.pdf
	modified:   draft.tex

\author{Yongxin Ge, 
        Xinyu Ren, 
        Chenqiu Zhao,
        Anup Basu
        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.}
        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.}
        }

>>>>

\author{Yongxin Ge, 
        Xinyu Ren, 
        Chenqiu Zhao, ~\IEEEmembership{Student Member,~IEEE}
        Anup Basu, ~\IEEEmembership{Senior Member,~IEEE}
        \thanks{Yongxin Ge is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.(e-mail: yongxinge@cqu.edu.cn)}
        \thanks{Xinyu Ren is with School of Software Engineering, Chongqing University, Chongqing (401331), PR China.(e-mail: hsinyujen@gmail.com)}
        \thanks{Chenqiu Zhao is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.(e-mail: zhao.chenqiu@ualberta.ca)}
        \thanks{Anup Basu is with Department of Computing Science, University of Alberta (T6G 2E1), Canada.(e-mail: basu@ualberta.ca)}
        }
